### 2017-11-16 Risk analysis/Text/Layout/Layout/chapter3_results.tex
Some text progress, new IE Figure

		\subsection{Posterior model III}%ML2
		\begin{figure}[p!]
			\centering
			\includegraphics[width=1\textwidth]{Figures/ML2}
			\caption{....}\label{fig:ML2}
		\end{figure}
		Results from this third model show that in contrast to the reservoir thickness, seal thickness is a primary and decisive factor for trap volume. Using likelihoods which favor a thick reservoir, might only a thin seal of about 50 m thickness, leakage due to  
		- see ML2: seal thickness as decisive factor
			-> if seal thin and reservoir thick see the ratio of both!), higher likelihood of surpassing SSF

>>>>

		\subsection{Posterior model III: Likely very thin seal}%ML2
		\begin{figure}[p!]
			\centering
			\includegraphics[width=1\textwidth]{Figures/ML2}
			\caption{....}\label{fig:ML2}
		\end{figure}
		Results from this third model show that in contrast to the reservoir thickness, seal thickness is a primary and decisive factor for trap volume. Using likelihoods which favor a thick reservoir, but only a thin seal of about 50 m thickness, leakage due to juxtaposition with seal-overlying formations across the fault becomes the primary mechanism for trap volume control (see Figure \ref{fig:ML2} (c). It can recognized in Figure \ref{fig:ML2} (b) that while uncertainty was reduced clearly in the footwall, it remains high in the hanging wall. The state of information entropy in furthermore suggests that the seal layer in the appeared often significantly deeper hanging wall than in the footwall. Combined with a generally very thin seal, this allowed for the occurrence of high displacement to seal thickness ratios, i.e. high Shale Smear Factors. Thus, a frequenting surpassing of the critical $SSF$ and subsequent fault seal breaching was enabled. It is additionally apparent in Figure \ref{fig:ML2} (b), that while fault-related leakage has become predominant, control by the spill point has become widely irrelevant in this posterior model.\\	%It is suggested by the footwall information entropy in Figure \ref{label} (b), that the general shape of the structure has been flattened.
		A dramatically higher probability of complete trap failure is induced by the high frequency of cross-fault leakage to overlying formations. Consequently, the bulk of the posterior $ROV$ probability distribution is dropped to a volume of zero, as depicted in Figure \ref{fig:ML2} (d). Any positive trap volumes have become highly improbable.\\
		Bayes actions changed accordingly. Given this posterior $ROV$ distribution, all actors find their minimum of expected loss at $ROV = 0$, which equals the decision to "take no action" (see Figure \ref{fig:ML2} (e)). It has to be pointed out that all Bayes actions are found at the same point, due to the lack of negative values, into which more risk-averse actors would presumably move, if given the possibility. Compared to the prior model, expected losses were decreased overall.
